---
title: "Field Results"
author: "Adam Ulicny"
date: "2024-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Results:
### Number of observed individuals
2023: 440
2024: 321
**SUM: 761**
### Number of foraging actions
2023 : 1717
2024: 1135
**SUM: 2852**
### Species observed:
### 2023
25 species total
**18** sufficiently sampled (n individuals > 2)
### 2024
20 species total
**15** sufficiently sampled (n individuals > 2)
### Combined dataset 2023+2024
25 species total
**20** sufficiently sampled! (n individuals >2)

# Differences between years
```{r Foraging between years, echo=FALSE}
library(gridExtra)
grid.arrange(method23, method24, substrate23, substrate24, foliage_23, foliage_24, distance_23, distance_24, ncol=4, nrow =2)
```

## Changes in specialization?
```{r Specialization between years, echo=FALSE}
plot(specialization_23)
plot(specialization_24)
```
### Note:
In the Index standardization formula, we use the number of categories (either substrate or method)
$ð‘©_ð‘¨ = ðŸ âˆ’ (ð‘© âˆ’ ðŸ)/(ð’ âˆ’ ðŸ)$
Should we base the n-categories on the theoretical categories or categories observed?

## Specialization for full dataset
```{r Specialization full dataset, echo=FALSE}
plot(specialization_full)
```
# Guilds (~2800 foraging actions total)
```{r Guilds with aesthetics, echo=FALSE}
par(mar=c(5,1,1,12))
plot(dendro_pretty, main = "Foraging guilds", type = "rectangle", horiz = T)
legend("topleft", 
       legend = labelLegend, 
       col = labelColors_2, 
       pch = c(20,20,20,20), bty = "y",  pt.cex = 1.5, cex = 0.8 , 
       text.col = "black", horiz = FALSE,
       title="Guilds",
       inset = c(0, 0.1))
```

```{r Guilds displayed in a different style, echo=FALSE}
library(factoextra)
fviz_dend(dendro, cex = 0.8, lwd = 0.8, k = 6,
                  rect = TRUE,
                  k_colors = "jco",
                  rect_border = "jco",
                  rect_fill = TRUE,
                  type = "phylogenic",
                  repel=T)
```

```{r Guild - Phylo tanglegram, echo=FALSE}
library(dendextend)
set.seed(12345)
dendlist(dendro_pretty, dendro_phylo_best)%>%
  dendextend::untangle(method="random", R=1000)%>%####### Crucial step to produce human readable codendrograms! Use lower R on slower machines.
  dendextend::untangle(method="step2side")%>%############## For troubleshooting, use "%>% entanglement()" to assess entanglement (lower is better)
  tanglegram(common_subtrees_color_lines = TRUE, # Do NOT include "sort=T" argument if using untangle before (sort overrides it)
             highlight_distinct_edges  = FALSE,
             highlight_branches_lwd=FALSE,
             margin_inner=10,
             margin_outer=7,
             lwd=3,
             main_left="behavior",
             main_right="phylogeny",
             hang=F)


legend("topleft", 
       legend = labelLegend, 
       col = labelColors_2, 
       pch = c(20,20,20,20), bty = "n",  pt.cex = 1.5, cex = 0.8 , 
       text.col = "black", horiz = FALSE, inset = c(0, 0.1))

```


